The main challenge, in this analysis, is to achieve reliable predictions of the low Standard Model background 
leading to the same-sign leptons + jets final state. 
This background is composed partly of rare processes such as the associate production of a top quark pair with a massive boson, 
or the production of multiple bosons. 
The other contribution consists in experimental backgrounds originating from the imperfect discrimination between prompt leptons and other objects, 
or the occasional misreconstruction of the electron charge. 
The following sections provide more details about the nature of these different categories of background, 
and the foreseen methods that will be used to estimate their contributions to the signal regions. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Backgrounds with prompt SS dilepton or three leptons}
\label{sec:bkg_prompt}

There are two main sources of Standard Model background leading to pairs of same-sign prompt leptons: 
\begin{itemize}
\item[$\bullet$] The associate production of top quark(s) and massive bosons, where the same-sign leptons pair 
originates from leptonic decays of one of the top quarks and of the boson. 
These processes are characterized by a large jet multiplicity, the presence of $b$-jet(s), 
and always have intrinsic missing momentum. 
Therefore they generally represent the largest contribution to the signal regions. 
The dominant processes are $pp\to t\bar{t}W(j)$, $pp\to t\bar{t}Z(j)$ and $pp\to t\bar{t}H$, 
while there are also minor contributions from $pp\to tZbj,\,t\bar{t}WW$, and $pp\to t\bar{t}t\bar{t}$. 
\item[$\bullet$] The production of multiple massive bosons. 
These processes have generally low jet multiplicities. 
However, due to their larger cross-sections, they contribute in a significant way to the background entering signal regions without $b$-jets requirements. 
The dominant processes include $pp\to W^\pm W^\pm jj,\,WZ,\,ZZ$, 
with minor contributions from $pp\to\,WH,\,ZH,\,VVV$ and $H\to\,ZZ\to\,\ell\ell\ell\ell$ or $H\to\,WW\to\,\ell\nu +X$. 
\end{itemize}

We estimate the contributions of these various processes to the signal regions by relying on the Monte-Carlo predictions, 
normalized with the best known theoretical cross-sections: these processes are too rare to allow use of control regions until a significant integrated luminosity will be collected. 
For example, in~\cite{Ducu:2021084} which establishes projections of the sensitivity 
to the $ttH$ signal strength in a final state very similar to this analysis, 
the impact of adding control regions for $t\bar t+V$ processes was found to be favorable only after collecting $\sim 100$~\ifb~of data. 

Processes containing top quarks ($\ttbar + X$) have cross-sections below 1~pb, which have consequently not yet been much constrained experimentally. On the theoretical side, uncertainties on the cross sections are typically large: 30\% for $t\bar{t}W$ and 50\% for $t\bar{t}Z$ for the same-sign $\sqrt{s}=7$~TeV analysis~\cite{NoteSS3L_7TeV}, 22\% for both $t\bar{t}W$ and $t\bar{t}Z$ for the $\sqrt{s}=8$~TeV analysis~\cite{noteSS3L}. 

Cross-sections for diboson processes are known with a rather good accuracy, but only for the inclusive processes, 
while we are mostly interested in processes where several additional partons are produced, 
which carry subsequent additional uncertainties. 

The validation regions described in section~\ref{sec:bkg_VR} help us to ensure that our understanding of these processes is sufficiently reliable, and that the systematic uncertainties assigned to the estimated rates are reasonable. 

%%%%%%%%%%%%%%%%%%
%\input{chFlip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Backgrounds with fake leptons: general information}
\label{sec:bkg_fakes} 
\input{bkg_fakes_general}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Backgrounds with fake leptons: the matrix method}
\label{sec:bkg_matrix_method}
\input{bkg_matrix_method}

